---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fable.tscount

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/fable.tscount)](https://CRAN.R-project.org/package=fable.tscount)
[![Codecov test coverage](https://codecov.io/gh/mitchelloharawild/fable.tscount/branch/master/graph/badge.svg)](https://codecov.io/gh/mitchelloharawild/fable.tscount?branch=master)
[![R build status](https://github.com/mitchelloharawild/fable.tscount/workflows/R-CMD-check/badge.svg)](https://github.com/mitchelloharawild/fable.tscount/actions)
<!-- badges: end -->

The `{fable.tscount}` package allows `tsglm()` models from the [`{tscount}`]((https://cran.r-project.org/package=tscount))
package to be used in a tidy workflow with the modelling interface of
'fabletools'. This extends 'tscount' to provide enhanced model
specification and management, performance evaluation methods, and
model combination tools.

## Installation

You can install the **development** version from
[GitHub](https://github.com/mitchelloharawild/fable.tscount)

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("mitchelloharawild/fable.tscount")
```


<!-- You can install the released version of fable.tscount from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("fable.tscount") -->
<!-- ``` -->

## Usage

```{r ecoli}
library(fable.tscount)
library(tsibble)
ecoli <- tsibble(
  week = yearweek(paste0(tscount::ecoli$year, " W", tscount::ecoli$week)),
  cases = tscount::ecoli$cases,
  index = "week"
) 
ecoli
```

```{r fit}
fit <- ecoli %>% 
  model(TSCOUNT(cases))
fit
```

```{r report}
report(fit)
```

```{r generate}
ecoli %>% 
  model(TSCOUNT(cases)) %>% 
  generate(times = 10)
```


## Code of Conduct

Please note that the fable.tscount project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
